---
title: "models"
author: "Zsófia Tóth"
date: '2018 december 10 '
output: html_document
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load the data}
# all.1 data without IGF outlier, all.2 data without cort outlier, all.3 data without IGF and cort outlier

load("/home/zsofci/Asztal/igf_plasticity/plasticity.RData")
```


```{r repeatability of food consuption, eval=FALSE, include=FALSE}
# we used only 3-3days per week, because on every week we got 2 days of very bad weather which could influence the measurements
hist(consupt_long$weight)
consupt_long$ring<-as.factor(consupt_long$ring)
consupt_long_new<-subset(consupt_long, day %in% c("d3", "d4", "d5", "d8","d9","d10")) 
hist(consupt_long_new$weight)

library(rptR)
rep1<-rpt(weight~(1|ring), grname = "ring", data=consupt_long, datatype = "Gaussian", nboot = 0, npermut = 0)
summary(rep1)
#plot(rep1, grname = "ring", type = "boot", cex.main = 0.8)


se <- function(x) sqrt(var(x)/length(x))

mean(consupt_long_new$weight) # 5.507
se(consupt_long_new$weight) # 0.052

```


# Compare the masses and conditions
```{r include=FALSE}
library(lme4)
library(lmerTest)
library(emmeans)
mass.model<-(lmer(mass~treat+ (1|ring), data=masscond))
anova(mass.model)
emmeans(mass.model, list(pairwise ~ treat), adjust = "tukey")

cond.model<-(lmer(cond~treat+ (1|ring), data=masscond))
anova(cond.model)
emmeans(cond.model, list(pairwise ~ treat), adjust = "tukey")
```

# Control group
## Difference between the 2 experimental week
```{r graphs in control groups}
library(lme4)
library(lmerTest)

resigf.cont1<-lmer(resigf~etap+(1|ring), data=t.all[t.all$treat=="C",]) # do not have difference between the 2 week
summary(resigf.cont1)
igf.cont1<-lmer(igf1~etap+(1|ring), data=t.all[t.all$treat=="C",])
summary(igf.cont1)
#resigf.cont2<-lmer(resigf.2~etap+(1|ring), data=t.all[t.all$resigf<30000 & t.all$treat=="C",]) # do not have difference between the 2 week
#rescort.cont<-lmer(rescort~etap+(1|ring), data=t.all[t.all$treat=="C",]) # do not have difference between the 2 week
mass.cont<-lmer(mass~etap+(1|ring), data=t.all[t.all$treat=="C",]) # mass was higher in the second experimental week
summary(mass.cont)
cond.cont<-lmer(cond~etap+(1|ring), data=t.all[t.all$treat=="C",]) # condition was higher in the second experimental week
summary(mass.cont)
glu.cont<-lmer(glu~etap+(1|ring), data=t.all[t.all$treat=="C",]) # glucose level was higher in the second experimental week
summary(glu.cont)
#ua.cont<-lmer(ua~etap+(1|ring), data=t.all[t.all$treat=="C",]) # do not have difference in the 2 experimental week
ékjdc
```

# The effect of the treatment
## IGF-1
```{r include=FALSE}
library(MuMIn)
all$group<-as.factor(all$group)

summary(lmer(igf1~treat*etap*group+(1|ring), data=all))
igf<-all[complete.cases(all$igf1),]

im1<-lmer(igf1~treat*etap*group+(1|ring), data=igf, na.action=na.fail)
d.im1<-dredge(im1)
summary(model.avg(d.im1))
print(d.im1) # model with lowest AIC and BIC value, do not contain significant p-value

summary(lmer(igf1~treat*etap*group+(1|ring), data=igf))
summary(lmer(igf1~treat*etap*group+(1|ring), data=igf))
summary(lmer(igf1~treat*etap+group+(1|ring), data=igf))
summary(lmer(igf1~treat+etap*group+(1|ring), data=igf))
summary(lmer(igf1~treat+etap+group+(1|ring), data=igf))

summary(lmer(igf1~treat+etap+(1|ring), data=igf))
summary(lmer(igf1~treat*etap+(1|ring), data=igf))
summary(lmer(igf1~treat*group+(1|ring), data=igf))
summary(lmer(igf1~treat+group+(1|ring), data=igf))
summary(lmer(igf1~etap*group+(1|ring), data=igf))
summary(lmer(igf1~etap+group+(1|ring), data=igf))

summary(lmer(igf1~etap+(1|ring), data=igf))
summary(lmer(igf1~group+(1|ring), data=igf))
summary(lmer(igf1~treat+(1|ring), data=igf))

# with cort and extraction IGF
summary(lmer(igf1~treat+group+sex+mass+cond+foodmean+extracted+ecortx+(1|ring), data=all))
drop1(lmer(igf1~treat+group+sex+mass+cond+foodmean+extracted+ecortx+(1|ring), data=all))

summary(lmer(igf1~treat+group+sex+mass+cond+extracted+ecortx+inject+(1|ring), data=all))
summary(lmer(igf1~treat+group+sex+mass+cond+extracted+ecortx+inject+(1|ring), data=all))
summary(lmer(igf1~treat+sex+mass+cond+extracted+ecortx+inject+(1|ring), data=all))
summary(lmer(igf1~treat+sex+mass+extracted+ecortx+inject+(1|ring), data=all))
summary(lmer(igf1~treat+sex+mass+extracted+inject+(1|ring), data=all))
summary(lmer(igf1~treat+sex+mass+inject+(1|ring), data=all))
summary(lmer(igf1~treat+mass+(1|ring), data=all))

all_noNA<-all[-c(1,28,96),]

all_noNA$fit_igf<-fitted(lmer(igf1~treat+mass+(1|ring), data=all_noNA))


#summary(lmer(igf1~treat*round+mass+(1|ring), data=all)) <- try with Pablo
```

```{r}
#Initial model, but nothing was significant in this structure
summary(lmer(igf1~treat*etap*group+(1|ring), data=igf))

#Initial model.2
summary(lmer(igf1~treat+group+sex+mass+cond+foodmean+extracted+ecortx+(1|ring), data=all))

#Final model
summary(lmer(igf1~treat+mass+(1|ring), data=all))
```


## Residual IGF-1
```{r eval=FALSE, include=FALSE}
summary(lmer(resigf~treat*etap*group+(1|ring), data=all))
resigf<-all[complete.cases(all$resigf),]

resim1<-lmer(resigf~treat*etap*group+(1|ring), data=resigf, na.action=na.fail)
d.resim1<-dredge(resim1)
summary(model.avg(d.resim1))
print(d.resim1)  # model with lowest AIC and BIC value, do not contain significant p-value

summary(lmer(resigf~treat*etap*group+(1|ring), data=all))
drop1(lmer(resigf~treat*etap*group+(1|ring), data=all))
summary(lmer(resigf~treat*etap+group+(1|ring), data=all))
summary(lmer(resigf~treat+etap*group+(1|ring), data=all))

summary(lmer(resigf~treat+etap+group+(1|ring), data=all))

summary(lmer(resigf~treat+etap+(1|ring), data=all))
summary(lmer(resigf~treat*etap+(1|ring), data=all))
summary(lmer(resigf~treat*group+(1|ring), data=all))
summary(lmer(resigf~treat+group+(1|ring), data=all))
summary(lmer(resigf~etap*group+(1|ring), data=all))
summary(lmer(resigf~etap+group+(1|ring), data=all))

summary(lmer(resigf~etap+(1|ring), data=all))
summary(lmer(resigf~group+(1|ring), data=all))
summary(lmer(resigf~treat+(1|ring), data=all))

# with other variables
summary(lmer(extracted~treat+group+sex+mass+cond+foodmean+igf1+ecortx+(1|ring), data=all))
drop1(lmer(extracted~treat+group+sex+mass+cond+foodmean+igf1+ecortx+(1|ring), data=all))
drop1(lmer(extracted~treat+group+sex+cond+foodmean+igf1+ecortx+(1|ring), data=all))
drop1(lmer(extracted~treat+group+cond+foodmean+igf1+ecortx+(1|ring), data=all))
drop1(lmer(extracted~treat+group+cond+foodmean+ecortx+(1|ring), data=all))
drop1(lmer(extracted~treat+group+cond+ecortx+(1|ring), data=all))
drop1(lmer(extracted~treat+cond+ecortx+(1|ring), data=all))
drop1(lmer(extracted~treat+cond+(1|ring), data=all))
drop1(lmer(extracted~treat+(1|ring), data=all))
summary(lmer(extracted~treat+(1|ring), data=all))
```

```{r}
summary(lmer(extracted~treat+(1|ring), data=all))
```


## Extracted IGF-1
```{r eval=FALSE, include=FALSE}
summary(lmer(extracted~treat*etap*group+(1|ring), data=all))
extracted<-all[complete.cases(all$extracted),]

em1<-lmer(extracted~treat*etap*group+(1|ring), data=extracted, na.action=na.fail)
d.em1<-dredge(em1)
summary(model.avg(d.em1))
print(d.em1)

summary(lmer(extracted~treat*etap*group+(1|ring), data=all))
drop1(lmer(extracted~treat*etap*group+(1|ring), data=all))
summary(lmer(extracted~treat*etap+group+(1|ring), data=all))
summary(lmer(extracted~treat+etap*group+(1|ring), data=all))
summary(lmer(extracted~treat+etap+group+(1|ring), data=all))
summary(lmer(extracted~treat+etap+(1|ring), data=all))
summary(lmer(extracted~treat*etap+(1|ring), data=all))
summary(lmer(extracted~treat*group+(1|ring), data=all))
summary(lmer(extracted~treat+group+(1|ring), data=all))
summary(lmer(extracted~etap+group+(1|ring), data=all))
summary(lmer(extracted~etap*group+(1|ring), data=all))
summary(lmer(extracted~group+(1|ring), data=all))
summary(lmer(extracted~etap+(1|ring), data=all))
summary(lmer(extracted~treat+(1|ring), data=all)) #marginally non significant

# with other variables
summary(lmer(extracted~treat+group+sex+mass+cond+foodmean+igf1+ecortx+(1|ring), data=all))
drop1(lmer(extracted~treat+group+sex+mass+cond+foodmean+igf1+ecortx+(1|ring), data=all))
summary(lmer(extracted~treat+group+sex+cond+foodmean+igf1+ecortx+(1|ring), data=all))
summary(lmer(extracted~treat+group+cond+foodmean+igf1+ecortx+(1|ring), data=all))
summary(lmer(extracted~treat+group+cond+foodmean+ecortx+(1|ring), data=all))
summary(lmer(extracted~treat+group+cond+ecortx+(1|ring), data=all))
summary(lmer(extracted~treat+cond+ecortx+(1|ring), data=all))
summary(lmer(extracted~treat+cond+(1|ring), data=all))
summary(lmer(extracted~treat+(1|ring), data=all))
```

```{r}
summary(lmer(extracted~treat+(1|ring), data=all))
```


## Corticosterone
```{r}
cort<-all[complete.cases(all$rescort.nooutlier),]
cm1<-lmer(rescort.nooutlier~treat*etap*group+(1|ring), data=cort, na.action = na.fail)
cd<-dredge(cm1)
print(cd) # best model was not significant

#summary(lmer(rescort.nooutlier~treat*etap*group+(1|ring), data=cort))
#drop1(lmer(rescort.nooutlier~treat*etap*group+(1|ring), data=cort))
drop1(lmer(rescort.nooutlier~treat*etap+group+(1|ring), data=cort)) #group was significant
#drop1(lmer(rescort.nooutlier~treat+etap*group+(1|ring), data=cort))
drop1(lmer(rescort.nooutlier~treat+etap+group+(1|ring), data=cort)) #group was significant

#drop1(lmer(rescort.nooutlier~treat+etap+(1|ring), data=cort))
#drop1(lmer(rescort.nooutlier~treat*etap+(1|ring), data=cort))
#drop1(lmer(rescort.nooutlier~treat*group+(1|ring), data=cort))
drop1(lmer(rescort.nooutlier~treat+group+(1|ring), data=cort)) # group was significant
#drop1(lmer(rescort.nooutlier~etap*group+(1|ring), data=cort))
drop1(lmer(rescort.nooutlier~etap+group+(1|ring), data=cort)) # group was significant

#drop1(lmer(rescort.nooutlier~etap+(1|ring), data=cort))
drop1(lmer(rescort.nooutlier~group+(1|ring), data=cort)) # significant
#drop1(lmer(rescort.nooutlier~treat+(1|ring), data=cort))


```
FINAL MODEL:
Fixed effects:
            Estimate Std. Error      df t value Pr(>|t|)  
(Intercept)  -1.3181     0.9439 58.3784  -1.397   0.1679  
groupTC       2.5767     1.2757 60.4847   2.020   0.0478 *
---
Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1


## Mass
```{r}
summary(lmer(mass~treat*etap*group+(1|ring), data=all))
mm1<-lmer(mass~treat*etap*group+(1|ring), data=all, na.action = na.fail)
summary(lmer(mass~treat*group+etap+(1|ring), data=all))
summary(lmer(mass~treat*group+(1|ring), data=all))

library(MuMIn)

d1<-dredge(mm1)
summary(model.avg(d1))
print(d1) 
# best model is if we gave 3 variable: 
summary(lmer(mass~treat*etap*group+(1|ring), data=all, na.action = na.fail))

#model selection for only 2 variable
#drop1(lmer(mass~treat*etap+group+(1|ring), data=all))
#drop1(lmer(mass~treat+etap*group+(1|ring), data=all))
mm2<-lmer(mass~treat+etap+group+(1|ring), data=all) # only significant
summary(mm2)

mm3<-lmer(mass~treat+etap+(1|ring), data=all) # only significant
summary(mm3)
#drop1(lmer(mass~treat*etap+(1|ring), data=all))
mm4<-lmer(mass~treat*group+(1|ring), data=all) # only significant
summary(mm4)

#drop1(lmer(mass~treat+group+(1|ring), data=all))
#drop1(lmer(mass~etap*group+(1|ring), data=all))
#drop1(lmer(mass~etap+group+(1|ring), data=all))

mm5<-lmer(mass~etap+(1|ring), data=all) # only siginifcant
summary(mm5)
#drop1(lmer(mass~group+(1|ring), data=all))
mm6<-lmer(mass~treat+(1|ring), data=all) #only significant
summary(mm6)

#check which is the best model from all significant model
anova(mm1,mm2,mm3,mm4,mm5,mm6)

```

### CONDITION
```{r eval=FALSE, include=FALSE}
summary(lmer(cond~treat+sex+igf1+foodmean+(1|ring), data=all))
drop1(lmer(cond~treat+sex+igf1+cond+foodmean+(1|ring), data=all))

summary(lmer(cond~treat+sex+foodmean+(1|ring), data=all))
drop1(lmer(cond~treat+sex+foodmean+(1|ring), data=all))

summary(lmer(cond~treat+foodmean+(1|ring), data=all))
drop1(lmer(cond~treat+foodmean+(1|ring), data=all))

summary(lmer(cond~treat+(1|ring), data=all))
drop1(lmer(cond~treat+(1|ring), data=all))

```

```{r}
plot(2)
```


# Delta hormones/mass/condition/treatment
```{r delta hormones and mass, eval=FALSE, include=FALSE}

# summary(lm(drescort~dmass, data=all[all$treat=="C",]))

# IGF
summary(lmer(digf~sex+dmass+foodmean+dcond+prev.mass+etap+group+prev.igf+(1|ring), data=all[all$treat=="C",]))

summary(lmer(digf~sex+dmass+foodmean+dcond+etap+group+(1|ring), data=all[all$treat=="C",]))

summary(lmer(digf~sex*(dmass+foodmean)+etap+group+(1|ring), data=all[all$treat=="C",]))

summary(lmer(digf~prev.igf+(1|ring), data=all[all$treat=="C",])) # I did not find significant effect

# mass
summary(lmer(dmass~digf+prev.mass+sex*foodmean+etap+group+(1|ring), data=all[all$treat=="C",]))
summary(lmer(dmass~group+(1|ring), data=all[all$treat=="C",]))

summary(lmer(dmass~prev.mass+(1|ring), data=all[all$treat=="C",])) # forward model selection


#condition
summary(lmer(dcond~prev.mass+sex*(foodmean+digf)+etap+group+(1|ring), data=all[all$treat=="C",]))
summary(lmer(dcond~group+(1|ring), data=all[all$treat=="C",]))


#summary(lm(dresigf~dmass, data=all[all$treat=="C",]))
#summary(lm(drescort~dresigf, data=all[all$treat=="C",]))

```

# Random slope/intercept
## IGF-1
```{r}
slopeIGFa.2<-lmer(igf1 ~ treat + (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=all[all$igf1<8000,])
slopeIGFa.3<-lmer(igf1~treat*etap+(1|ring), control=lmerControl(optimizer="bobyqa"), data=all[all$igf1<8000,])
slopeIGFa.4<-lmer(igf1~treat*etap+(treat|ring), control=lmerControl(optimizer="bobyqa"), data=all[all$igf1<8000,])
slopeIGFa.5<-lmer(igf1 ~ treat * etap + (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=all[all$igf1<8000,])
slopeIGFa.6<-lmer(igf1 ~ treat *etap+ (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=all[all$igf1<8000,]) 
slopeIGFa.7<-lmer(igf1~treat+(1|ring), control=lmerControl(optimizer="bobyqa"), data=all[all$igf1<8000,])
#            Df    AIC    BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)    
#slopeIGFa.7  4 1551.8 1561.9 -771.89   1543.8                             


slopeIGFa.8<-lmer(igf1~treat+(treat|ring), control=lmerControl(optimizer="bobyqa"), data=all[all$igf1<8000,])
#            Df    AIC    BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)    
#slopeIGFa.8  6 1552.9 1568.0 -770.43   1540.9 0.3363      0     <2e-16 ***

slopeIGFa.9<-lmer(igf1 ~ treat+ (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=all[all$igf1<8000,])
anova(slopeIGFa.4,slopeIGFa.2, slopeIGFa.3, slopeIGFa.5, slopeIGFa.6, slopeIGFa.7, slopeIGFa.8, slopeIGFa.9)
```


## Extracted IGF-1
```{r}
# slopeIGFe.2<-lmer(extracted ~ treat + (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=all) # singular fit
slopeIGFe.3<-lmer(extracted~treat*etap+(1|ring), control=lmerControl(optimizer="bobyqa"), data=all)
slopeIGFe.4<-lmer(extracted~treat*etap+(treat|ring), control=lmerControl(optimizer="bobyqa"), data=all)
#slopeIGFe.5<-lmer(extracted ~ treat * etap + (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=all) # numreically singular
#slopeIGFe.6<-lmer(extracted ~ treat *etap+ (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=all) # numerically singular
slopeIGFe.7<-lmer(extracted~treat+(1|ring), control=lmerControl(optimizer="bobyqa"), data=all)
#            Df    AIC    BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
#slopeIGFe.7  4 387.22 395.53 -189.61   379.22     

slopeIGFe.8<-lmer(extracted~treat+(treat|ring), control=lmerControl(optimizer="bobyqa"), data=all)
#            Df    AIC    BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)
#slopeIGFe.3  6 389.95 402.42 -188.98   377.95 1.2608      2     0.5324

#slopeIGFe.9<-lmer(extracted ~ treat+ (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=all) #singular fit
#anova(slopeIGFe.4,slopeIGFe.2, slopeIGFe.3, slopeIGFe.5, slopeIGFe.6, slopeIGFe.7, slopeIGFe.8, slopeIGFe.9)
anova(slopeIGFe.4,slopeIGFe.3,slopeIGFe.7, slopeIGFe.8)

```


## residual IGF-1
```{r}
library(lmerTest)
#igf.1<-lmer(resigf.2~cond+rescort+mass.change+sex+order+(1+treat|ring)+(1+treat|etap), data=t.all, 
#             control = lmerControl(optimizer ="bobyqa")) # with the huge IGF-1 values
#drop(igf.1) # no significant effect

#igf.2<-lmer(resigf~cond+rescort+mass.change+sex+order+(1+treat|ring)+(1+treat|etap), data=t.all, REML=FALSE, control = lmerControl(
#                           optimizer ="bobyqa")) # without the huge IGF-1 values
#drop(igf.2) # no significant effect


#SLOPES for only if we have handling time
library(nlme)
#slopeIGF<-lmer(resigf ~ treat + (treat|ring)+(ring|etap), control=lmerControl(optimizer="bobyqa"), data=t.all)

slopeIGF.2<-lmer(resigf ~ treat + (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=t.all)
slopeIGF.3<-lmer(resigf~treat*etap+(1|ring), control=lmerControl(optimizer="bobyqa"), data=t.all)
slopeIGF.4<-lmer(resigf~treat*etap+(treat|ring), control=lmerControl(optimizer="bobyqa"), data=t.all)
slopeIGF.5<-lmer(resigf ~ treat * etap + (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=t.all)
slopeIGF.6<-lmer(resigf ~ treat *etap+ (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=t.all) 
slopeIGF.7<-lmer(resigf~treat+(1|ring), control=lmerControl(optimizer="bobyqa"), data=t.all)
slopeIGF.8<-lmer(resigf~treat+(treat|ring), control=lmerControl(optimizer="bobyqa"), data=t.all)
#             Df    AIC    BIC  logLik deviance  Chisq Chi Df Pr(>Chisq) 
# slopeIGF.8  6 1043.4 1056.2 -515.72   1031.4 3.6423      0     <2e-16 ***

slopeIGF.9<-lmer(resigf ~ treat+ (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=t.all)
anova(slopeIGF.4,slopeIGF.2, slopeIGF.3, slopeIGF.5, slopeIGF.6, slopeIGF.7, slopeIGF.8, slopeIGF.9)
```

## residual CORT
```{r}
#cort.1<-lmer(rescort~cond+resigf+mass.change+sex+order+(1+treat|ring)+(1+treat|etap), data=t.all, REML=FALSE, control = lmerControl(
#                           optimizer ="bobyqa")) # with the huge IGF-1 values
#drop(cort.1) # no significant effect

#SLOPES
#slopeCORT<-lmer(rescort ~ treat + (treat|ring)+(ring|etap), control=lmerControl(optimizer="bobyqa"), data=t.all)
slopeCORT.2<-lmer(rescort ~ treat + (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=t.all)
#slopeCORT.3<-lmer(rescort~treat*etap+(1|ring), control=lmerControl(optimizer="bobyqa"), data=t.all)
#slopeCORT.4<-lmer(rescort~treat*etap+(treat|ring), control=lmerControl(optimizer="bobyqa"), data=t.all)
#slopeCORT.5<-lmer(rescort ~ treat * etap + (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=t.all)
#slopeCORT.6<-lmer(rescort ~ treat *etap+ (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=t.all) 
slopeCORT.7<-lmer(rescort~treat+(1|ring), control=lmerControl(optimizer="bobyqa"), data=t.all)
#            Df    AIC    BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)    
#slopeCORT.7  4 397.39 406.03 -194.70   389.39 

slopeCORT.8<-lmer(rescort~treat+(treat|ring), control=lmerControl(optimizer="bobyqa"), data=t.all)
#            Df    AIC    BIC  logLik deviance  Chisq Chi Df Pr(>Chisq)    
#slopeCORT.8  6 400.83 413.78 -194.42   388.83 0.1441      0     <2e-16 ***

slopeCORT.9<-lmer(rescort ~ treat+ (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=t.all)
#anova(slopeCORT.4,slopeCORT.2, slopeCORT.3, slopeCORT.5, slopeCORT.6, slopeCORT.7, slopeCORT.8, slopeCORT.9)
anova(slopeCORT.2, slopeCORT.7, slopeCORT.8, slopeCORT.9)
```

## Mass and condition
```{r}
#SLOPE for Mass
#slopeMASS<-lmer(mass ~ treat + (treat|ring)+(ring|etap), control=lmerControl(optimizer="bobyqa"), data=all) #túl bonyolult modell
slopeMASS.2<-lmer(mass ~ treat + (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=all)
#            Df    AIC    BIC   logLik deviance  Chisq Chi Df Pr(>Chisq)    
#slopeMASS.2  7 210.50 228.45  -98.248   196.50 14.0363      1  0.0001793 ***

slopeMASS.3<-lmer(mass~treat*etap+(1|ring), control=lmerControl(optimizer="bobyqa"), data=all)
#            Df    AIC    BIC   logLik deviance  Chisq Chi Df Pr(>Chisq)    
#slopeMASS.3  6 204.88 220.27  -96.443   192.88 18.8894      2  7.911e-05 ***

slopeMASS.4<-lmer(mass~treat*etap+(treat|ring), control=lmerControl(optimizer="bobyqa"), data=all)
#            Df    AIC    BIC   logLik deviance  Chisq Chi Df Pr(>Chisq)    
#slopeMASS.4  8 206.98 227.49  -95.488   190.98  5.5207      1  0.0187925 *  

slopeMASS.5<-lmer(mass ~ treat * etap + (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=all)
slopeMASS.6<-lmer(mass ~ treat *etap+ (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=all) 
slopeMASS.7<-lmer(mass~treat+(1|ring), control=lmerControl(optimizer="bobyqa"), data=all)
slopeMASS.8<-lmer(mass~treat+(treat|ring), control=lmerControl(optimizer="bobyqa"), data=all)
slopeMASS.9<-lmer(mass ~ treat+ (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=all)
anova(slopeMASS.4,slopeMASS.2, slopeMASS.3, slopeMASS.5, slopeMASS.6, slopeMASS.7, slopeMASS.8, slopeMASS.9)

#SLOPE for condition
#slopeCOND<-lmer(cond ~ treat + (treat|ring)+(ring|etap), control=lmerControl(optimizer="bobyqa"), data=t.all)
slopeCOND.2<-lmer(cond ~ treat + (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=all)
#            Df    AIC    BIC  logLik deviance   Chisq Chi Df Pr(>Chisq)    
#slopeCOND.2  7 234.76 252.71 -110.38   220.76 14.4463      1  0.0001442 ***

slopeCOND.3<-lmer(cond~treat*etap+(1|ring), control=lmerControl(optimizer="bobyqa"), data=all)
#            Df    AIC    BIC  logLik deviance   Chisq Chi Df Pr(>Chisq)    
#slopeCOND.3  6 231.06 246.44 -109.53   219.06 17.2409      2  0.0001804 ***

slopeCOND.4<-lmer(cond~treat*etap+(treat|ring), control=lmerControl(optimizer="bobyqa"), data=all)
#            Df    AIC    BIC  logLik deviance   Chisq Chi Df Pr(>Chisq)    
#slopeCOND.4  8 231.49 252.00 -107.74   215.49  5.2694      1  0.0217030 *  

slopeCOND.5<-lmer(cond ~ treat * etap + (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=all)
slopeCOND.6<-lmer(cond ~ treat *etap+ (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=all) 
slopeCOND.7<-lmer(cond~treat+(1|ring), control=lmerControl(optimizer="bobyqa"), data=all)
slopeCOND.8<-lmer(cond~treat+(treat|ring), control=lmerControl(optimizer="bobyqa"), data=all)
slopeCOND.9<-lmer(cond ~ treat+ (treat|ring)+(1|etap),control=lmerControl(optimizer="bobyqa"), data=all)
anova(slopeCOND.4,slopeCOND.2, slopeCOND.3, slopeCOND.5, slopeCOND.6, slopeCOND.7, slopeCOND.8, slopeCOND.9)

```

# Best random structures
```{r}
slopeIGF.end<-lmer(igf1~treat*(sex+mass+foodmean)+(treat|ring), control=lmerControl(optimizer="bobyqa"), data=all)
summary(lmer(igf1~treat+mass+(treat|ring), control=lmerControl(optimizer="bobyqa"), data=all))

```

# Effect of previous injection
```{r igf and food consuption}
summary(lmer(digf~inject+(1|ring), data=all[all$group=="CT",]))
summary(lmer(digf~group*inject+(1|ring), data=all))

#summary(lmer(extracted~inject+(1|ring), data=all))
#summary(lmer(igf1~inject+(1|ring), data=all))
#summary(lmer(rescort.nooutlier~inject+(1|ring), data=all))
#summary(lmer(mass~inject+(1|ring), data=all))
```

# repeatability in hormones
## IGF-1
```{r igf}
library(rptR)
igfrep<-rpt(igf1~(1|ring), grname = c("ring"), data=all[all$treat=="C",], datatype = "Gaussian", nboot = 0, npermut = 0)
summary(igfrep)
#plot(igfrep, grname = "ring", type = "boot", cex.main = 0.8)

igfrept<-rpt(igf1~(1|ring) + treat, grname = c("ring"), data=all, datatype = "Gaussian", nboot = 0, npermut = 0)
summary(igfrept)
#plot(igfrept, grname = "ring", type = "boot", cex.main = 0.8)
```

## residual IGF-1
```{r resigf}
library(rptR)
resigfrep<-rpt(resigf~(1|ring), grname = c("ring"), data=all[all$treat=="C",], datatype = "Gaussian", nboot = 0, npermut = 0)
#plot(igfrep, grname = "ring", type = "boot", cex.main = 0.8)
summary(resigfrep)

resigfrept<-rpt(resigf~(1|ring) + treat, grname = c("ring"), data=all, datatype = "Gaussian", nboot = 0, npermut = 0)
summary(resigfrept)
#plot(igfrept, grname = "ring", type = "boot", cex.main = 0.8)
```

## extracted IGF-1
```{r extr igf}
library(rptR)
extractedrep<-rpt(extracted~(1|ring), grname = c("ring"), data=all[all$treat=="C",], datatype = "Gaussian", nboot = 0, npermut = 0)
#plot(igfrep, grname = "ring", type = "boot", cex.main = 0.8)
summary(extractedrep)

extractedrept<-rpt(extracted~(1|ring) + treat, grname = c("ring"), data=all, datatype = "Gaussian", nboot = 0, npermut = 0)
#plot(igfrept, grname = "ring", type = "boot", cex.main = 0.8)
summary(extractedrept)
```

## CORT
```{r cort}
library(rptR)
rescortrep<-rpt(rescort.nooutlier~(1|ring), grname = c("ring"), data=all[all$treat=="C",], datatype = "Gaussian", nboot = 0, npermut = 0)
#plot(igfrep, grname = "ring", type = "boot", cex.main = 0.8)
summary(rescortrep)

rescortrept<-rpt(rescort.nooutlier~(1|ring) + treat, grname = c("ring"), data=all, datatype = "Gaussian", nboot = 0, npermut = 0)
#plot(igfrept, grname = "ring", type = "boot", cex.main = 0.8)
summary(rescortrept)
```

